Self Regulation Ontology Retest Data: Initial Exploration

### 2017-02-15 SRO_Retest_Analyses.Rmd
cont working on retest exploration

@@

 Can you get the factor structure for the retest
 step 1:Ttest on all measures of T1 for people w and without retest
 step2 : efa on the people you don't have retest on and then predict how well this holds up for people w retest on t1 and on t2
T1 comparison for people who came back vs didn't (of all that are invited)

>>>>

Data cleaning for efa
```{r}
#read in only meaningful vars
meaningful_var_test <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_clean.csv')

meaningful_var_retest <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/meaningful_variables_clean.csv')

#Process sub_id columns in the data dataframes
meaningful_var_retest$X <- as.character(meaningful_var_retest$X)
meaningful_var_test$X <- as.character(meaningful_var_test$X)

names(meaningful_var_retest)[1] <- 'sub_id'
names(meaningful_var_test)[1] <- 'sub_id'

#Clean and subset dfs as before
meaningful_var_retest <- meaningful_var_retest %>%
  group_by(sub_id) %>%
  do(correct_subids(.,test_worker_lookup))

#Are all retest subjects in test_data? No. 
sum(meaningful_var_retest$sub_id %in% meaningful_var_test$sub_id) == nrow(meaningful_var_retest)

#Who is missing?
meaningful_var_retest$sub_id[which(meaningful_var_retest$sub_id %in% meaningful_var_test$sub_id == FALSE)]

#Remove sub w missing test data from retest data
retest_data_mngf <- meaningful_var_retest[meaningful_var_retest$sub_id %in% meaningful_var_test$sub_id,]

#Extract test data for subs w retest data
retest_subs_test_mngf <- meaningful_var_test[meaningful_var_test$sub_id %in% meaningful_var_retest$sub_id,]

#Extract test data for subs without retest data (efa df)
rest_subs_test_mngf <- meaningful_var_test[meaningful_var_test$sub_id %in% meaningful_var_retest$sub_id == FALSE,]

#Arrange datasets of same size by sub_id
retest_data_mngf = retest_data_mngf %>% arrange(sub_id)
retest_subs_test_mngf = retest_subs_test_mngf %>% arrange(sub_id)

#CHECK IF EVERYTHING IS ORDERED RIGHT
retest_subs_test_mngf$sub_id == retest_data_mngf$sub_id
```

Checking columns for efa:
NEED TO RESOLVE SOME DIFFERENCES IN MEANINGFUL VARS BETWEEN THE TWO DATASETS
```{r}
#Check columns 
names(retest_data_mngf)[names(retest_data_mngf) %in% names(retest_subs_test_mngf) == FALSE]

names(retest_subs_test_mngf)[names(retest_subs_test_mngf) %in% names(retest_data_mngf) == FALSE]

#Subset datasets with only matching columns
all_columns_mngf <- unique(c(names(retest_data_mngf), names(retest_subs_test_mngf)))

matching_columns_mngf <- c()
for(i in 1:length(all_columns_mngf)){
  if(all_columns_mngf[i] %in% names(retest_data_mngf) & all_columns_mngf[i] %in% names(retest_subs_test_mngf)){
    matching_columns_mngf <- c(matching_columns_mngf, all_columns_mngf[i])
  }
}

retest_data_mngf <- retest_data_mngf[,matching_columns_mngf]
retest_subs_test_mngf <- retest_subs_test_mngf[,matching_columns_mngf]
rest_subs_test_mngf <- rest_subs_test_mngf[,matching_columns_mngf]

#standardize all vars going in to factor analysis
rest_subs_test_mngf_z <- rest_subs_test_mngf

for(i in 1:length(rest_subs_test_mngf)){
  if(names(rest_subs_test_mngf)[i] == 'sub_id'){
    rest_subs_test_mngf_z$sub_id = rest_subs_test_mngf$sub_id
  }
  else{
    rest_subs_test_mngf_z[,names(rest_subs_test_mngf)[i]] = scale(rest_subs_test_mngf[,i])
  }
}
```

Efa on subjects from original dataset withOUT retest data (using meaningful vars only)
```{r}
unrotated <- efaUnrotate(rest_subs_test_mngf_z, nf=3, varList=names(rest_subs_test_mngf_z)[-1], estimator="mlr")

summary(unrotated, std=TRUE)
inspect(unrotated, "std")
```

```{r}
library(psych)
corMat <- cor(rest_subs_test_mngf_z)
solution <- fa(r = corMat, nfactors = 2, rotate = "oblimin", fm = "pa")
```

@@

 Can you get the factor structure for the retest
 step 1:Ttest on all measures of T1 for people w and without retest
 step2 : efa on the people you don't have retest on and then predict how well this holds up for people w retest on t1 and on t2

T1 comparison for people who came back vs didn't (of all that are invited)
